Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
bit more of the paper done

>>>>

To allow our protocol to be utilized via Pidgin, we needed our plugin to interface with two major aspects of the protocol: the discovery server, and the libmotmot library.

\subsection{Plugin Interactions with Discovery Server}

\subsection{Plugin Interactions with Libmotmot}
There were a few major difficulties that had to be addressed when calling libmotmot within the plugin:

\begin{itemize}
\item libpurple makes a distinction between "IMs" (two-person chats) and "chats" (three or more people); libmotmot does not.  libpurple takes in different arguments for its IM-related and its chat-related functions

\item One cannot modify the main Pidgin event loop from within a plugin (without patching libpurple itself).  Instead, callbacks are made to plugin functions from within the main event loop, so finding a way to call libmotmot functions correctly (i.e. still honoring the correct control flow from libmotmot's perspective) and consistently within the bounds of these plugin functions was a second challenge.

\end{itemize}
